Mathematical Aspects of the Capital Market

### 2014-05-08 thesis/thesis.tex
Change the section about Nordea 15min in 1st quarter 2012.

\section{Collection of Figures and Tables}
\begin{figure}[htb!]
  \centering
  \subfigure[ACF of $z_t$]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_quotient_acf.pdf}
    \label{fig:nordea_15min_quotient_acf}
  }
  \subfigure[ACF of $z_t^2$]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_quotient_squared_acf.pdf}
    \label{fig:nordea_15min_quotient_squared_acf}
  }
  \caption{\small \it Nordea 15min $z_t$ and $z_t^2$ auto-correlation
    function (ACF).}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Normal Probability Plot of $y_t$]{
    \includegraphics[scale=0.4, clip=true, trim=76 256 109
    214]{../pics/nordea2_y_normplot.pdf}
    \label{fig:nordea_15min_y_qq}
  }
  \subfigure[ACF of $y_t$]{
    \includegraphics[scale=0.4, clip=true, trim=92 258 104
    218]{../pics/nordea_15min_y_acf.pdf}
    \label{fig:nordea_15min_y_acf}
  }
  \caption{\small \it Nordea 15min $y_t$ normal probability plot and
    autocorrelations}
\end{figure}

>>>>

\section{Collection of Figures and Tables}

\begin{figure}[htb!]
  \centering
  \subfigure[]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_acf.pdf}
    \label{fig:nordea_15min_acf}
  }
  \subfigure[]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_vlt_acf.pdf}
    \label{fig:nordea_15min_vlt_acf}
  }
  \caption{\small \it Auto-correlations among Nordea Bank 15min
    returns. \ref{fig:nordea_15min_acf}: Auto-correlations (ACF) of the
    squared returns; \ref{fig:nordea_15min_vlt_acf}: Auto-correlations
    (ACF) of squared realized volatilities ($\hat{\sigma}^2_t$).}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[ACF of $z_t$]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_quotient_acf.pdf}
    \label{fig:nordea_15min_quotient_acf}
  }
  \subfigure[ACF of $z_t^2$]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_quotient_squared_acf.pdf}
    \label{fig:nordea_15min_quotient_squared_acf}
  }
  \caption{\small \it Nordea 15min $z_t$ and $z_t^2$ auto-correlation
    function (ACF).}
\end{figure}

% \begin{figure}[htb!]
%   \centering
%   \subfigure[Normal Probability Plot of $y_t$]{
%     \includegraphics[scale=0.4, clip=true, trim=76 256 109
%     214]{../pics/nordea2_y_normplot.pdf}
%     \label{fig:nordea_15min_y_qq}
%   }
%   \subfigure[ACF of $y_t$]{
%     \includegraphics[scale=0.4, clip=true, trim=92 258 104
%     218]{../pics/nordea_15min_y_acf.pdf}
%     \label{fig:nordea_15min_y_acf}
%   }
%   \caption{\small \it Nordea 15min $y_t$ normal probability plot and
%     autocorrelations}
% \end{figure}
